Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-03-06 ms.tex
I adjusted the baseline in the equation from additive to multiplicative times a 1 + variation which makes very little difference. I updated the relevant time series and amplitude spectra plots.
I added the original light curves to an appendix for the interested reader.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
	\label{fig:tserPfold}
\end{figure*}

@@

Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.

As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -2.7~hr and +1.3~hr.
In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.

Each of the light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + \\
B t + C + D a(t)
\end{split}
\end{equation}
where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

@@

%\appendix

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity.
	Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
	\label{fig:tserDetrend}
\end{figure*}

@@

Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserDetrend}.
The baseline trends (which scale linearly with time and linearly with airmass) have been removed from Figure~\ref{fig:tserDetrend}, but the original light curves can be viewed in Figure \ref{fig:tserNoDetrend}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.

As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -2.7~hr and +1.3~hr.
As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.

Each of the light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

@@

\appendix

\section{Original Light Curves}

We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
The linear baseline terms as a function of time and airmass in Equation \ref{eq:cosfit} fit the baseline variations not due to the brown dwarf variations.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_tser_no_detrend.pdf}
	\label{fig:tserPhase0835NoDetrend}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_tser_no_detrend.pdf}
	\label{fig:tserPhase1821NoDetrend}
	}
	\caption{Time series for each system with an offset added for clarity, as in Fig \ref{fig:tserDetrend}, but in this case showing the raw light curves without de-trending.
	Each wavelength bin is labeled on the right side. Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near telluric absorption features at 1.38$\mu$m and 1.87$\mu$m.}
	\label{fig:tserNoDetrend}
\end{figure*}
